---
title: "NMwateR-NEWS"
author: "Ben.Block@tetratech.com"
date: "`r Sys.time()`"
output: github_document
  #md_document:
   # variant: markdown_github
---

<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

# NMwateR 1.0.0 (2025-12-15)
-   Small updates per Erik Leppo's review
-   Prep for first GitHub release
-   To do:
    -   Have NMED review functionality
    -   Add verbose arguments
    
# NMwateR 0.0.0.9067 (2025-12-08)
-   Fixed examples to run using loaded example files
-   To do:
    -   Have NMED review functionality

# NMwateR 0.0.0.9066 (2025-12-08)

-   Used testthat to make internal tests for every function
-   To do:
    -   Have NMED review functionality
    
# NMwateR 0.0.0.9062 (2025-12-03)

-   Added pkgdown and R-CMD-Check
-   To do:
    -   Have NMED review functionality
    -   Use testthat to make internal tests
    
# NMwateR 0.0.0.9056 (2025-11-24)

-   Added vignette
-   Updated nutrients (lakes) logic per instructions from NMED
-   To do:
    -   Have NMED review functionality
    -   Use testthat to make internal tests
    -   Set up GitHub tests

# NMwateR 0.0.0.9053 (2025-11-17)

-   Added all functions from NMED R project as of 11/07/2025
-   To do:
    -   Have NMED review functionality
    -   Use testthat to make internal tests
    -   Set up GitHub tests
    -   Add vignette

# NMwateR 0.0.0.9000 (2025-11-07)

-   Initial development
